Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-11-28 dsn-2018/bare_conf.tex
Outline changes

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Alexander M. Scheel}
\IEEEauthorblockA{Iowa State University\\
Ames, IA, USA \\
Email: alexander.m.scheel@gmail.com}
\and
\IEEEauthorblockN{Eric W. D. Rozier}
\IEEEauthorblockA{Iowa State University\\
Ames, IA, USA \\
Email: erozier@iastate.edu}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

@@

\section{Terminology \& Notation}

@@

\section{Broader Impacts}

@@

\section{Open Research}

@@

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Alexander M. Scheel, Eric W. D. Rozier}
\IEEEauthorblockA{Department of Computer Science\\Iowa State University of Science and Technology\\
Ames, Iowa, USA 50011\\
Email: \texttt{alexander.m.scheel@gmail.com, erozier@iastate.edu}}}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

\textbf{The contributions of this paper are...}

\begin{itemize}
\item We...
\end{itemize}

@@

The remainder of this paper is organized as follows... In Section
\ref{Sec:Terminology} we...

\section{Related Work}
\label{Sec:Related}

Broad context... intersection... subsection introductions.

\subsection{Differential Cryptanalysis}

\subsection{Satisfiability Solving}

\section{Terminology \& Notation}
\label{Sec:Terminology}

@@

\section{Discussion}

@@

@@

\section{Future Work}
